### 2008-09-15 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ should be able to see the changes made by $op_i$ unless data has been changed by a more recent precedessor  \\

@@

Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.

Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.//

proof: If the data is not valid anymore it means the data has changed since $t_{i-1}$. This implies at least one operation $b$ has chaged the data since the use. $b$ is either a succesor in the same transaction or a different one. According to Def 1 and Def 3, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem. Hence $b$ belongs to a different transaction namely $T_j$. Since $T_j$ should have already commited, according to Rule 6 all operation in $OP_{T_i}$ should succed those in $OP_{T_j}$, however, we know there is at least an operation $a$ that does not succced $b$ (since it has not seen the "changes" made by $b$). Hence, $T_i$ can not commit.\\

@@

Assumption: Each operation has an offset status assioated with it. We call this operation.offsetstatus\\

Assumption: An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant. An operation with absolute offset means the value is absolute and does not depend on any other operation OR the operation only specifies a specific value for the offset for the next operation (i.e. seek). An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transactions. \\

@@

2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.

@@

@@

1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4.

@@

%proof: A write operation writes to the most recently commited offset (unless imposed otherwise by a seek or a prior read or a following read as shown above) of the file descriptor.  According to Def 2, it does not "use" any data. Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known. 
Now we will describe the components of our system and demosntrate how the algorithm

>>>>

Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ sees the changes made by $op_i$ unless data has been changed by a more recent precedessor. Furthermore  \\

@@

Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.\\

Principle 0: An operation should not see any modifications other than those made by precedessors (either in the same transaction or others)\\

proof: Obviously such modifications are not valid and are probably part of a faulty operation.\\

Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.\\

proof: If the data is not valid anymore it means the data has changed since $t_{i-1}$. This implies at least one operation $b$ has chaged the data since the use. $b$ is either a succesor (since the changes were not seen) in the same transaction or a different one. According to Def 1 and Def 3, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem. Hence $b$ belongs to a different transaction namely $T_j$. Since $T_j$ should have already commited, according to Rule 6 all operation in $OP_{T_i}$ should succed those in $OP_{T_j}$, however, we know there is at least an operation $a$ that does not succced $b$ (since it has not seen the "changes" made by $b$). Hence, $T_i$ can not commit.\\

@@

Assumption: Each operation has a offset status assioated with it. We call this operation.offsetstatus. Each operation has a data satus assosiated with it namely operation.datastatus\\

Assumption:  An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant. An operation with absolute offset means the value is absolute and does not depend on any other operation OR the operation only specifies a specific value for the offset for the next operation (i.e. seek). An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transaction and not being valid at commit instant\\

Assumption: Based on previous assumptions read.datastatus = Defenite and others are Speculative, hence they do not use the "file contents"

@@

2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.\\

@@

Req 5: An operation with datastatus = Defenite, converts all the speculative offsttypes of the previous operations to Defenite. This requirement is always enforced.\\

proof: Since if datastatus = Defenite, this mean the operation is "using" or "reading" some file contents- an irreversible action- and as this operation should be able to see the modifications made by all preceding operations, if these are speculative, at commit instant they may "relocate" their modifications, this means eitehr $op$ may not see some changes made by precedessors or may see some changes not made by any precedessors (since the speculatively changes were used by $op$ however these did not get reflected in the actual file system since they were relocated at commit instant). Either way contradicts the defenitions and principles (Def 8 and Principle 0).\\

Note: Req 5 suggest if datatype = Definite this causes all the previous operation with Speculative as offsettype to be changed to Defenite.

@@

4- After doing the above check if datastatus = Defenite, then change all offsettypes in the input that are Speculative to Defenite in the output.

1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4. 4 also ensures Req 5.

@@

%proof: A write operation writes to the most recently commited offset (unless imposed otherwise by a seek or a prior read or a following read as shown above) of the file descriptor.  According to Def 2, it does not "use" any data. Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known. 
Now we will describe the components of our system and demosntrate how the algorithm conforms to the function just described, and how all the rules principles are gurantedd.
